### 2017-03-30 paper/evaluation.tex
adjusted scripts from RQ2

\Jbc{pending updates! $\rightarrow$}
Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  However, parallelism by itself does
not assure speedups on those projects.  One sensible factor that is
important to the effectiveness of low-level parallelism is the
distribution of test costs in the test suite.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

@@

    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{R/testcost-med.pdf}
      \caption{\label{fig:medtcost}Medium}
    \end{subfigure}\\

    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{R/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long}
    \end{subfigure}%

    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Medium & 17 & 20 & 7 \\
        Long   &  9 & 14 & 5 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}...\Fix{Looks like there are missing
        projects...}}    
    \end{subfigure}%

    \caption{\label{fig:time-distributions}Distribution of time cost per project.}    
\end{figure}

>>>>

\Jbc{Pending updates here}
Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  However, parallelism by itself does
not assure speedups on those projects.  One sensible factor that is
important to the effectiveness of low-level parallelism is the
distribution of test costs in the test suite.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

@@

    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-med.pdf}
      \caption{\label{fig:medtcost}Medium group}
    \end{subfigure}\\

    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group}
    \end{subfigure}\\

    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Medium & 17 & 20 & 7 \\
        Long   &  9 & 14 & 5 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}\Fix{missing caption}}    
    \end{subfigure}%

    \caption{\label{fig:time-distributions}Distribution of test case
    execution cost per project.}    
\end{figure}
